---
title: 'Case Study: Data Analysis of COVID-Spread in South Korea'
author: "Mair, Thangavelu, Türmen"
date: "23/01/2021"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width = 12, fig.height = 4, fig.align = "center")
```
# Introduction

In December 2019, a contagious disease (COVID-19) started to spread worldwide leading to the ongoing pandemic. The disease is caused by severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2), which belongs to the family of corona viruses. The first case was identified in Wuhan, China and the virus started spreading quickly (1). The virus spreads from one person to another when they are in close contact through aerosols transmitted from an infected person when they speak, sing, breathe, cough, sneeze (2). However the exact route of transmission is rarely proven (3). 

South Korea was one of the first countries to identify the virus outside China, with the first cases being reported in January 2020. The government of South Korea was alert and started to implement measures to restrict the spread of the virus. The measures include, but not restricted to mass testing of population, contact tracing to track and isolate potentially infected persons. The data collected by Korea Centers for Disease Control & Prevention was used to create a structured data set (5).

In this short analysis, the above-mentioned data was used to visualize the spread of the virus and subsequently develop claims regarding the pandemic. For this purpose techniques of data analysis including visualization and statistical testing was conducted using the programming language R.

> "Data analysis is a process of inspecting, cleansing, transforming and modeling data with the goal of discovering  useful informaiton, informing conclusions and supporting decision-making (4)."

This report presents the results of Data analysis conducted on the data from KCDC. It is divided into the following sections. The first section provides an overview of the data along with the code and  the second section provides the observations from the statistical analysis.



# Data Visualisation
## Load Essential Libraries
In order to analyse the data, the following libraries were used.

```{r message=FALSE}
library(data.table)
library(magrittr)
library(tidyr) 
library(dplyr)
library(ggplot2)
library(devtools)
library(patchwork) # Draw multiple graphs at once
library(GGally) # Correlation
library(tidyverse) # for str_replace

# the following are for the geographical maps
library(ggmap)
library(maps)
library(mapdata)
library(raster)

```

## Graph Theme

In order to maintain the same theme for all the graphs, a theme was defined as 
follows

```{r themes}
ThemeMain <-theme(panel.background=element_rect(fill="white"),
                  title = element_text(size=14, face='bold'),
                  axis.text.y =  element_text(color='black',size=10), 
                  axis.text.x = element_text(color='black',size=10),
                  axis.title.x = element_text(size=12,color='black'),
                  axis.title.y = element_text(size=12,color='black'),
                  plot.title = element_text(hjust = 0.5),
                  legend.title = element_text(size=12,color='black'),
                  legend.background = "white") + theme_bw()


# the following theme is used for the spatial map
map_theme <- theme(axis.ticks = element_blank(),axis.text = element_blank(),
                   axis.title = element_blank(),
                   panel.background=element_rect(fill="white"))

```

## Tidy Data

The following data were loaded from (5).

```{r message=FALSE}
case_dt <- fread("data/Case.csv")
patient_info_dt <- fread("data/PatientInfo.csv")
policy_dt <- fread("data/policy.csv")
region_dt <- fread("data/Region.csv")
search_trend_dt <- fread("data/SearchTrend.csv")
seoul_floating_dt <- fread("data/SeoulFloating.csv")
time_dt <- fread("data/Time.csv")
time_age_dt <- fread("data/TimeAge.csv")
time_gender_dt <- fread("data/TimeGender.csv")
time_province_dt <- fread("data/TimeProvince.csv")
weather_dt <- fread("data/Weather.csv")
```

All date data were converted to "date" data-type in Year-Month-Day format.

All categorical data was converted to "factor". 

Integer and double data were converted to their data types  

Required columns were renamed.

The summary of all data tables were displayed to get a feel for the data and its
distribution. It includes understanding the maximum, minimum, and average of 
all the variables present in the data.

Data tables were merged appropriately to facilitate the visualization process 
and the subsequent statistical testing

```{r warning=FALSE}

# Data type conversion for case_dt
case_dt[, `:=` (province = as.factor(province),
                latitude = as.double(latitude),
                longitude = as.double(longitude))]
#summary(case_dt)
```

```{r echo=FALSE,message=FALSE,warning=FALSE}

# Data type conversion for patient_info_dt
patient_info_dt[, `:=` (sex = as.factor(sex),
            age = as.factor(age),
            infected_by = as.integer(infected_by),
            contact_number = as.integer(contact_number),
            symptom_onset_date = as.Date(symptom_onset_date, format="%Y-%m-%d"),
            confirmed_date = as.Date(confirmed_date, format="%Y-%m-%d"),
            released_date = as.Date(released_date, format="%Y-%m-%d"),
            deceased_date = as.Date(deceased_date, format="%Y-%m-%d"),
            state = as.factor(state))]
#summary(patient_info_dt)

# Data type conversion for policy_dt
policy_dt[, `:=` (type = as.factor(type),
                  start_date = as.Date(start_date, format="%Y-%m-%d"),
                  end_date = as.Date(end_date, format="%Y-%m-%d"))]
#summary(policy_dt)

# Data type conversion for region_dt
region_dt[, province := as.factor(province)]
#summary(region_dt)

# Data type conversion for search_trend_dt
search_trend_dt[, date := as.Date(date, format="%Y-%m-%d")]
#summary(search_trend_dt)

# Data type conversion for seoul_floating_dt
seoul_floating_dt[, `:=` (date = as.Date(date, format="%Y-%m-%d"),
                          sex = as.factor(sex))]
setnames(seoul_floating_dt, "hour", "time")
#summary(seoul_floating_dt)

# Data type conversion for time_dt
time_dt[, date := as.Date(date, format="%Y-%m-%d")]
summary(time_dt)

# Data type conversion for time_age_dt
time_age_dt[, `:=` (date = as.Date(date, format="%Y-%m-%d"),
                    age = as.factor(age))]
#summary(time_age_dt)

# Data type conversion for time_gender_dt
time_gender_dt[, `:=` (date = as.Date(date, format="%Y-%m-%d"),
                       sex = as.factor(sex))]
#summary(time_gender_dt)

# Data type conversion for time_province_dt
time_province_dt[, `:=` (date = as.Date(date, format="%Y-%m-%d"),
                         province = as.factor(province))]
summary(time_province_dt)

# Data type conversion for weather_dt
weather_dt[, `:=` (date = as.Date(date, format="%Y-%m-%d"),
                   province = as.factor(province))]
#summary(weather_dt)

```

## Visualisations
Plotting is crucial to data science because:
*It facilitates making new observations by discovering associations or patterns
in data.
*It facilitates communicating findings.
*Only relying on summary statistics is dangerous because it reduces data into a 
single number and carry much less information than a 2D representation.
*It helps debugging either bugs in the code through visual inspection.

<!-- ### Geographical distribution of number of cases -->
<!-- ```{r warning=FALSE, echo=FALSE} -->

<!-- skorea <- getData("GADM", country = "South Korea", level = 2) -->
<!-- skorea <- fortify(skorea) -->

<!-- province_location <- region_dt[province==city][province!="Korea",.(province,latitude,longitude)] -->

<!-- # extracting name and location of provinces with high cases -->
<!-- high_cases_province <- time_province_dt[,tot_confirmed:=sum(confirmed,na.rm=T),by=.(province)][1:17,][order(-tot_confirmed)] -->

<!-- name_province_high_cases <- as.matrix(high_cases_province[1:5,.(province)]) -->
<!-- name_location_province_high_cases <- province_location[province %in% name_province_high_cases] -->

<!-- # plot map with high # cases -->
<!-- ggplot() +   -->
<!--   geom_map(data = skorea, map = skorea, aes(x=long,y=lat, map_id=id,group=group),fill=NA,color="gray") +  -->
<!--   geom_point(data=case_lat_long_dt,aes(x=longitude,y=latitude,size=confirmed, color= "red",alpha=.5)) + -->
<!--   coord_fixed(ratio = 0.8) + -->
<!--   scale_size(range = c(2,7))+ -->
<!--   geom_text(data=name_location_province_high_cases,aes(x=longitude,y=latitude,label=province)) + -->
<!--   map_theme +  -->
<!--   guides(color=FALSE,alpha=FALSE) -->
<!-- ``` -->

<!-- From the above spatial distribution, it can be observed that the Covid-19 cases -->
<!-- were concentrated in two major cities:Seoul and Busan. -->

### Total Number of Cases
First, the total number of infections were plotted in a time series.

```{r echo=FALSE,warning=FALSE}

cases_by_date_dt <- time_province_dt[, .(
confirmed = sum(confirmed),
released = sum(released),
deceased = sum(deceased)
), by = c("date")]

cases_by_date_melted_dt <- melt(
cases_by_date_dt,
measure.vars = c("confirmed", "released", "deceased"),
variable.name = "status",
value.name = "count"
)

# Spread Rate of Corona in South Korea
plot_cases_cumulative <- ggplot(cases_by_date_melted_dt, 
                                aes(date, count, color = status)) +
                              geom_line(size = 1, show.legend = F) +
                              ggtitle("COVID-19 Cases in South Korea") +
                              xlab("Date") + 
                              ylab("Number of Patients") +
                              #scale_y_log10() +
                              ThemeMain
plot_cases_cumulative


```

The above plot displays the cumulative number of cases. It does not provide the 
full picture of the situation that was prevailing in South Korea. Therefore,
the cumulative data was converted into incremental and is displayed in the
following figure

```{r echo=FALSE,warning=FALSE}
# converting cumulative data into incremental

# converting cumulative into incremental
# time data table
time_d2d_dt <- copy(time_dt)

time_d2d_dt <- time_d2d_dt[,`:=`(test_d2d=c(test[1],diff(test,differences = 1)),
                                 negative_d2d=c(negative[1],
                                              diff(negative,differences = 1)),
                                 confirmed_d2d=c(confirmed[1],
                                              diff(confirmed,differences = 1)),
                                 released_d2d=c(confirmed[1],
                                              diff(released,differences = 1)),
                                 deceased_d2d=c(confirmed[1],
                                              diff(deceased,differences = 1)))]

# province data table
time_province_d2d_dt <- copy(time_province_dt)

time_province_d2d_dt <- time_province_d2d_dt[,`:=`
                (confirmed_d2d=c(confirmed[1],diff(confirmed,differences = 1)),
                   released_d2d=c(confirmed[1],diff(released,differences = 1)),
                   deceased_d2d=c(confirmed[1],diff(deceased,differences = 1))),
                by=.(province)]


#converting age_dt from cumulative to incremental
time_age <- time_age_dt[,confirmed_d2d:=c(confirmed[1],diff(confirmed)),
                        by=age][,deceased_d2d:=c(deceased[1],diff(deceased)),
                                by=age]

#ggplot(time_age,aes(date,confirmed_d2d)) + geom_bar(stat="identity") + facet_wrap(~age,scales = "free")

#converting gender_dt form cumulative to incremental
time_gender <- copy(time_gender_dt)

time_gender <- time_gender_dt[,confirmed_d2d:=c(confirmed[1],                                                           diff(confirmed)),by=sex][,deceased_d2d:=c(deceased[1],
                                                        diff(deceased)),by=sex]

```


```{r echo=FALSE, warning=FALSE}
time_d2d_cases_dt <- time_d2d_dt[, c("date", "confirmed_d2d", 
                                     "released_d2d", "deceased_d2d")]

time_d2d_cases_dt <- melt(
time_d2d_cases_dt,
measure.vars = c("confirmed_d2d", "released_d2d", "deceased_d2d"),
variable.name = "status",
value.name = "count"
)

plot_cases_d2d <-
ggplot(time_d2d_cases_dt, aes(date, count, color = status)) +
geom_line(size = 1) +
ggtitle("COVID-19 Cases in South Korea\n on a day-by-day basis") +
xlab("Date") +
ylab("Number of Patients") +
#scale_y_log10() +
ThemeMain

plot_cases_d2d
```
From the plot, it can be observed that there was a sudden surge in the number of
infections in February 2020 and afterwards the number of daily infections 
dropped. This plot shows that the steps taken by the government was effective
in bringing down the daily infections.

### Number of Cases per Province
As we have a sight of how the virus spread in time, it is essential for us to 
understand the number of infections across the different provinces. This 
representation will provide the information of which provinces were most 
affected by the pandemic. This representation provides the timeline of the 
infections in different provinces.

```{r echo=FALSE,warning=FALSE}
#converting the cumulative data into incremental
time_province_d2d_dt <- copy(time_province_dt)

time_province_d2d_dt <-
  time_province_d2d_dt[, `:=`(
    confirmed_d2d = c(confirmed[1], diff(confirmed, differences = 1)),
    released_d2d = c(released[1], diff(released, differences = 1)),
    deceased_d2d = c(deceased[1], diff(deceased, differences = 1))
  ), by = .(province)]


plot_cases_by_province_d2d <- ggplot(time_province_d2d_dt , 
                                aes(date, confirmed_d2d, color= province)) + 
                                geom_point(size=1.5) +
                                 ggtitle("Number of cases by Province\n 
                                         on a day-by-day basis")+
                                xlab("Date") + 
                               ylab("Number of Positively Tested Patients") + 
                                #scale_y_log10() +
                                ThemeMain

plot_cases_by_province_d2d

```
It can be observed that Daegu was the most affected province followed by 
Seoul. The other provinces have almost equal distribution of cases. 

```{r echo=FALSE, warning=FALSE}
province_tot_cases <- time_province_d2d_dt[, `:=`(tot_confirmed=sum(confirmed_d2d),
                                              tot_released = sum(released_d2d),
                                              tot_deceased = sum(deceased_d2d)),
                                       by=.(province)][1:17]

ggplot(province_tot_cases,aes(y=reorder(province,tot_confirmed),x=tot_confirmed)) + geom_bar(stat="identity") + 
  geom_text(aes(label=as.character(tot_confirmed)),hjust=-0.5) +
  xlab("Total Number of Cases (-)") + 
  ylab("Province") + 
  ggtitle("Number of Confirmed Cases per Province") + 
  ThemeMain

```
The 5 provinces with the highest number of cases can be observed from the plot.
The provinces are 
1. Daegu
2. Gyeongsangbuk-do 
3. Seoul
4. Gyeonggi-do
5. Incheon

The same plot was performed for the highest number of deaths. It was observed 
that the number of deaths per province followed the same order as that of the 
confirmed cases.
```{r echo=FALSE, warning=FALSE}

ggplot(province_tot_cases,aes(y=reorder(province,tot_deceased),x=tot_deceased)) + geom_bar(stat="identity") + 
  geom_text(aes(label=as.character(tot_deceased)),hjust=-0.5) +
  xlab("Total Number of Cases (-)") + 
  ylab("Province") + 
  ggtitle("Number of Deceased Cases per Province") + 
  ThemeMain
```

### Age and Gender
The most frequent speculation during this pandemic was whether age/gender played
a role in determining the persons getting infected. In order to visualize this 
effect the following plots were used.
```{r echo=FALSE, warning=FALSE}
gender_vs_age <- patient_info_dt[,c("sex","age")]
level_age <- gender_vs_age
level_age$age <- factor(level_age$age, 
                        levels = paste0(seq(0,100,by = 10), "s"))
level_age <- level_age[ sex == c("female", "male") & age != ""]
level_age <- level_age[, confirmed := .N, by= c("sex", "age")]

# Confirmed cases by gender vs age in South Korea

ggplot(level_age, aes(age, confirmed)) + 
  geom_bar(stat = 'identity', width = 0.5,aes(fill=sex),position="dodge") +
  #geom_boxplot() +
  #facet_grid(~sex)+ 
  ggtitle("Gender vs Age") + 
  xlab("Age") + ylab("Confirmed Cases") + ThemeMain
```
> It can be observed that the gender/age of the person play an important role in 
getting infected. This claim will be further investigated by a statistical test.

> Will this be the case for patient deaths?

To visualise this effect, the number of deaths in each group was plot facetted 
by the gender in each age group.

```{r echo=FALSE, warning=FALSE}
# Deceased Patients per Sex in South Korea
# More Men than Women died
deaths_per_sex <- patient_info_dt[state == "deceased", .N , by = "sex"]
ggplot(deaths_per_sex[sex!=""], aes(sex, N)) + geom_bar(stat = "identity",width = 0.2) + 
  ggtitle("Deceased Patients per Sex") + xlab("Sex of Patients") + ylab("Number of Patients Deceased") + ThemeMain
```
When the data is plotted only for gender, it seems that higher number of female
patients deceased than the male patients. Sometimes such data can be misleading.
A third variable, in this case age, was introduced and data was visualized again

```{r echo=FALSE, warning=FALSE}
deaths_per_sex_and_age <- patient_info_dt[state == "deceased" & sex != "", .N , by = c("age", "sex")]

ggplot(deaths_per_sex_and_age, aes(age, N, fill = sex)) + geom_bar(stat = "identity", position="dodge", width = .7) + 
  ggtitle("Deceased Patients per Sex and Age") + xlab("Age of Patients") + ylab("Number of Patients Deceased") + ThemeMain
```
The above plot shows that the number of deceased female patients was higher only
in the age group of 80. In other age groups, number of deceased male patients 
is high. 

> It also shows that number of deceased patients was higher for the older patients
This claim was further investigated using a statistical test


### Weather

Another lasting speculation was about the weather and if it had any influence on
the number of infections or deaths. The weather includes average temperature,
precipitation, wind speed, etc. 

From the data, the temporal variation of temperature and the number of cases was
visualised. 
```{r echo=FALSE, warning=FALSE}
covid_vs_weather <- merge(weather_dt ,time_province_dt, 
                          by = c("date", "province"))

average_weather_dt <- covid_vs_weather[, .(avg_temp = mean(avg_temp, na.rm=T),
                                           min_temp = mean(min_temp, na.rm=T),
                                           max_temp = mean(max_temp, na.rm=T),
                                           precipitation = mean(precipitation, na.rm=T),
                                           max_wind_speed = mean(max_wind_speed, na.rm=T),
                                           most_wind_direction = mean(most_wind_direction, na.rm=T),
                                           avg_relative_humidity = mean(avg_relative_humidity, na.rm=T),
                                           confirmed = sum(confirmed),
                                           released = sum(released),
                                           deceased = sum(deceased)), by = "date"]

average_weather_melted_dt <- melt(average_weather_dt,
                                  measure.vars = c("confirmed", "released", "deceased"),
                                  variable.name = "status",
                                  value.name = "count")

average_weather_melted_dt <- melt(average_weather_melted_dt,
                                  measure.vars = colnames(average_weather_melted_dt[,-c("date","status","count")]),
                                  variable.name = "weather_condition")

filtered_weather <- average_weather_melted_dt[weather_condition == "avg_temp" | 
                                                weather_condition == "min_temp" | 
                                                weather_condition == "max_temp",]

# Temperature Changes in South Korea
plot_daily_temperature <- ggplot(filtered_weather,
             aes(date, value, color = weather_condition)) + geom_line() + 
             ggtitle("Temperature Changes in South Korea")+xlab("Date") + 
              ylab("Temperature") + 
             ThemeMain
plot_daily_temperature

# Arrange plot layout
# p3 + p4 + plot_layout(ncol = 1, heights = c(2,1.5))

plot_cases_cumulative + plot_daily_temperature + plot_layout(ncol=1) 

```

The above plot shows the temperature and the cumulative caes in South Korea.

> This cumulative cases show that temperature does have a correlation with the
number of infections. But in reality, this is not the case.

The same plot was repeated for incremental number of cases. It can be observed 
that temperature does not correlate with the number of infections. This will be
supported with a statistical test.

```{r echo=FALSE, warning=FALSE}

plot_cases_d2d + plot_daily_temperature + plot_layout(ncol = 1)

plot_daily_temperature + (plot_cases_cumulative + plot_cases_d2d + plot_layout(ncol=2)) + plot_layout(nrow = 2)
```

### Recovery and Decease Time for patients
Another important factor to be considered in this pandemic is the recovery time
of the patients. This adds to the burden on the hospitals. If the patients have
a longer recovery time, then the influx of new patients will increase the burden
of the hospitals.

> It would be helpful to understand the recovery time of different patients and
if the recovery time depends on the age/gender of the patients. This claim will 
be investigated further with a statistical test

Here, the visualization of the data is provided.
```{r echo=FALSE, warning=FALSE}

patients_per_time <- copy(patient_info_dt)
patients_per_time <- patients_per_time[, `:=` (desease_time = 
                                    as.integer(deceased_date - confirmed_date),
                                               desease_time_sym = as.integer(difftime(deceased_date, symptom_onset_date, units ="days")),
                                               recovery_time = as.integer(difftime(released_date, confirmed_date, units = "days")),
                                               recovery_time_sym = as.integer(difftime(released_date, symptom_onset_date, units ="days")))]


ggplot(patients_per_time[age!=""],aes(as.factor(age),recovery_time))+ 
  geom_boxplot(aes(middle=mean(desease_time))) +
  ggtitle("Age vs Recovery-time") +
  xlab("Age of Patients (years)") + 
  ylab("Time taken to recover (days)") + 
  ThemeMain

```
It is not clear from the above graph if age has any correlation with the 
average recovery time of the patient. This claim will be further investigated 
with a statistical test

The same plot was repeated for gender of the patients. It can be inferred that 
there is no difference between gender and recovery time of patients.

```{r echo=FALSE, warning=FALSE}
patients_per_time_melted_age_gender <- melt(patients_per_time, id.vars = c("sex", "age"), measure.vars = c("recovery_time", "desease_time"),
                                 variable.name = "status",
                                 value.name = "days")

patients_per_time_melted_age_gender <- patients_per_time_melted_age_gender[, .N, by=c("sex", "age", "status", "days")]

patients_per_time_melted_age_gender <- patients_per_time_melted_age_gender[days != is.na(days) & age != "",]

patients_per_time_melted_age_gender <- separate(patients_per_time_melted_age_gender, col = status, into = c("status","time"))
patients_per_time_melted_age_gender <- patients_per_time_melted_age_gender[, -"time"]

patients_per_time_melted_age_gender_recovery <- patients_per_time_melted_age_gender[status == "recovery",]

ggplot(patients_per_time_melted_age_gender_recovery, aes(sex, days)) + 
  geom_boxplot(aes(middle=mean(days))) + 
  xlab("Gender of patients") + 
  ylab("Recovery time of patients (days)") + 
  ggtitle("Recovery Time Vs Gender") + 
  ThemeMain
```
### Major Spreaders
As the virus spreads from person to person, it is important to trace the persons
who were in contact with an infected person. KCDC also provided trace data and 
this data was used to determine the type of patients who were spreading the 
virus.

> Do young people spread the virus? or Do male patients spread the virus?
How do people spread the virus?

Answering some of the above questions, will help in implementing impactful
policies in future.

```{r echo=FALSE, warning=FALSE}

# Overview of infection cases
infection_overview <- patient_info_dt[infection_case != "" & 
                                        infection_case != "etc" & sex != "" & 
                                        age != "", .N, 
                                      by = c("sex", "age", "infection_case",
                                             "infected_by")][order(-N)]


infected_by_overview <- infection_overview[infected_by != "", .N, by = c("age", "infected_by")][order(-N)]
infected_by_overview <- infected_by_overview %>% group_by(age)
#plot overview of spreading gender
overview_spreader <- merge(patient_info_dt, infected_by_overview, 
                           by.x = "patient_id", by.y = "infected_by", 
                           all.y = TRUE)


#general overview of spreading genders and age groups
overview_spreader_gender <- overview_spreader %>% 
  group_by(sex) %>% 
  summarise(sex_count = n())

overview_spreader_age <- overview_spreader %>% 
  group_by(age.x) %>% 
  summarise(age.x_count = n())

overview_spreader_age_gender <- overview_spreader[sex != "" & 
                                                    sex != is.na(sex) & 
                                                    age.x != "" & 
                                                    age.x != is.na(age.x),]

overview_spreader_age_gender <- overview_spreader_age_gender %>% 
  group_by(sex, age.x) %>% 
  summarise(age_count = n())

ggplot(overview_spreader_gender[2:3,], aes(sex, sex_count, fill = sex)) + 
  geom_bar(stat = "identity", position = "dodge", width = .2) +
  ggtitle("Genders vs Spread of the virus") + 
  xlab("Sex") + 
  ylab("Number of Spreads") + 
  ThemeMain
```

When the number of spreaders were plotted with the gender, it was observed that
males transmit the virus more than females. But when plotted with a third 
variable such as age, it is no longer the case. It is inferred that females in 
the age group of 50 transmitted the virus most often, according to the data.
This claim was further investigated using a statistical test

```{r echo=FALSE, warning=FALSE}
#plot overview of spreading gender and age groups (third variable effect)
ggplot(overview_spreader_age_gender, aes(age.x, age_count, fill = sex)) + 
  geom_bar(stat = "identity", position = "dodge", width = .7) +
  ggtitle("Age Groups and Genders that spread the virus") + 
  xlab("Age Group") +
  ylab("Number of Spreads") + 
  ThemeMain

```

KCDC also included the scenario under which the transmission took place. The 
following plot shows the major scenarios for each age group and gender

```{r echo=FALSE,message=FALSE, warning=FALSE}
# Split the overview of infection cases per Gender into top 3
infection_overview_top3_sex <- infection_overview %>% group_by(sex, infection_case) %>% summarise(count = n()) %>% top_n(n=3, wt = count)

# plot top 3 infection cases per gender
ggplot(infection_overview_top3_sex, aes(infection_case, count, fill = sex)) + geom_bar(stat = "identity", position = "dodge", width = .7) +
  ggtitle("Top 3 Infection Cases per Gender") + xlab("Infection Case") + ylab("Number of Infections") + ThemeMain

# Split the overview of infection cases per Age into top 3
infection_overview_top3_age <- infection_overview %>% group_by(age, infection_case) %>% summarise(count = n()) %>% top_n(n=3, wt = count)

#change order of levels
infection_overview_top3_age$age <- ordered(infection_overview_top3_age$age, levels = c("0s", "10s", "20s", "30s", "40s", "50s", "60s", "70s", "80s", "90s", "100s"))

# plot top 3 infection cases per age
ggplot(infection_overview_top3_age, aes(age, count, fill = infection_case)) + geom_bar(stat = "identity", width = .7) +
  ggtitle("Top 3 Infection Cases per Age") + xlab("Age") + ylab("Number of Infections") + ThemeMain

```

# Statistical Test
Statistical tests work by calculating a test statistic – a number that describes
how much the relationship between variables in your test differs from the null 
hypothesis of no relationship.

An important factor to consider when applying a statistical test is to check 
whether the data on which the test is applied conforms to the assumptions of
the test.

In this study, a correlation test is applied to test if one quantitative 
variable has an effect on the other continuous variable. Hence, a Q-Q plot is 
used to confirm if the data follows the distribution assumed by the test. 
For example, the spearman's rank correlation test (6) assumes that the data 
follows a normal distribution.

## Gender and number of cases
To test where there is a correlation between the gender and the number of 
recorded cases, the wilcoxson test was performed.

Gender is a categorical variable whereas number of recored cases is a 
quantitative variable and to test a relationship between such two variables, 
the t-test is preferred. However, to apply the t-test, the distribution of data
within the two categorical variable should be normal. In order to test if this 
assumption holds, a Q-Q plot was used as shown below

```{r}

qqplot_males <- ggplot(time_gender[sex=="male"],aes(sample=confirmed_d2d)) + 
  stat_qq() + 
  stat_qq_line(col="red",show.legend = T) + 
  xlab("Theorectical Normal distribution") + 
  ylab("Number of confirmed cases") + 
  ggtitle("Q-Q Plot for number of cases among Males") + 
  ThemeMain

qqplot_females <- ggplot(time_gender[sex=="female"],aes(sample=confirmed_d2d)) + 
  stat_qq() + 
  stat_qq_line(col="red",show.legend = T) + 
  xlab("Theorectical Normal distribution") + 
  ylab("Number of confirmed cases") + 
  ggtitle("Q-Q Plot for number of cases among Females") + 
  ThemeMain

qqplot_males + qqplot_females + plot_layout(ncol=2)

```
It can be observed that although the data follows a normal distribution, there
are outliers and because of the presence of outliers, t-test cannot be applied
in this case. Hence a wilcoxson test was used.

>The null hypothesis was stated as follows: Gender does not play an important
role in number of recorded cases.

```{r}
gender_tst_wilcox <- wilcox.test(data=time_gender,confirmed_d2d~sex)
gender_tst_wilcox$p.value 
```

The P-value was obtained to be 0.46, which is greater than 0.05(our alpha value
for determining the validity of null hypothesis). 
As the P-value is greater than 0.05, the null hypothesis was rejected.
Thus, a particular gender is not expected to be affected more.

## Average Recovery Time Vs Age
We have seen from section 2.2 that the recovery time is greater for older people.
To test this statistical significance of this observation, a statistical test
is performed. The spearman's rank correlation test is choosen for this purpose.

> Spearman's correlation test is a non-parametric measure of rank correlation
((statistical dependence between the rankings of two variables). It assesses 
how well the relationship between two variables can be described using a 
monotonic function (6).

This test eliminates the effect of outliers on the correlation. In our data, 
the average recovery time of age 100 is an outlier because it has only one 
observation. Therefore, this test is best-suited for this purpose.

```{r warning=FALSE}
decease_dt_age_num <- patients_per_time[,age:=str_replace(age,"s","")][,age:=
                                                                         as.integer(age)]
# statistical testing to support the observation ----------------------------
# H0: the average time for recovery is the same across all age groups
ggplot(patients_per_time[age!=""],aes(as.factor(age),recovery_time))+ 
  geom_boxplot(aes(middle=mean(desease_time))) +
  ggtitle("Age vs Recovery-time") +
  xlab("Age of Patients (years)") + 
  ylab("Time taken to recover (days)")

# Using aov to find correlation between the age group and average time of recovery in each group
recovery_age_aov_new <- patients_per_time[age!="",aov(recovery_time~as.factor(age))]
summary(recovery_age_aov_new) # 2e-16 < 0.005 => reject null

# convert age into num and find the correlation 
recovery_age_cor_new <- decease_dt_age_num[,cor.test(age,recovery_time,method="spearman")]

ggplot(decease_dt_age_num,aes(age,recovery_time)) + 
  geom_point() + 
  stat_smooth(method = lm) + 
  geom_label(x=10,y=90,label=paste("Spearman=",round(recovery_age_cor_new$estimate,2))) +
  ggtitle("Correlation between age and recovery time of patient") +
  xlab("Age of patients") + 
  ylab("Time taken to recover (days)") + 
  ThemeMain

```
The correlation coefficient is 0.16. It shows that there is a small positive
correlation between recovery time of patients. However, this coefficient is
low and it is not enough to conclude this observation. More data is required.

## Average Decease Time Vs Age
The same statistical test was conducted to verify the correlation between the 
age of the patient and decease time.

```{r warning=FALSE}
decease_age_cor_new <- decease_dt_age_num[,cor.test(age,desease_time,method="spearman")]

ggplot(decease_dt_age_num,aes(age,desease_time)) + 
  geom_point() + 
  stat_smooth(method = lm) + 
  geom_label(x=60,y=50,label=paste("Spearman=",round(decease_age_cor_new$estimate,2))) +
  ggtitle("Correlation between age and decease time of patient") +
  xlab("Age of patients") + 
  ylab("Time between disease-confirmation and decease")


```

The correlation coefficient is 0.27, which signifies a stronger correlation with
age compared to the recovery time. 

## Number of Deceased Vs Age
The spearman correlation test performed between age and number of deceased 
cases revealed that there is a strong positive correlation between them. 
However, in this study the exact age of the patient is not know. Only the 
number of cases in a particular age group is known. With this information, there
seems to be a positive correlation but more information is needed to confirm
this observation.

```{r}
# correlation test ----------------------------------------------------------
# age vs total number of confirmed cases and number of deaths
time_age_num <- time_age %>% mutate(str_replace(time_age$age,"s",""))
time_age_num <-time_age_num[,age:=NULL]
sn <- names(time_age_num)[1:6]
names(time_age_num) <- c(sn,"age")
time_age_num <- time_age_num[,age:=as.numeric(age)]


time_age_num <- time_age_num[,tot_confirmed:=sum(confirmed_d2d),by=.(age)]
time_age_num <- time_age_num[,tot_deceased:=sum(deceased_d2d),by=.(age)]


time_age_num_cor_dt <- time_age_num[1:9,.(age,tot_confirmed,tot_deceased)]

age_num_cor <- time_age_num_cor_dt[,cor.test(age,tot_confirmed,method = "spearman")]

age_num_cor_de <- time_age_num_cor_dt[,cor.test(age,tot_deceased,method = "spearman")]

ggplot(time_age_num_cor_dt,aes(age,tot_confirmed)) + 
  geom_point() + geom_smooth(method = lm) + 
  geom_label(x=20,y=2500,label=paste("Spearman=",round(age_num_cor$estimate,2)))+ 
  xlab("Age of Patients (years)") +
  ylab("Total Number of Confirmed Cases (-)") +
  ggtitle("Age Vs Total Number of Confirmed Cases") +
  ThemeMain

ggplot(time_age_num_cor_dt,aes(age,tot_deceased)) + 
  geom_point() + 
  geom_smooth(method = lm) + 
  geom_label(x=20,y=100,label=paste("Spearman=",round(age_num_cor_de$estimate,2)))+ 
  xlab("Age of Patients (years)") +
  ylab("Total Number of Deaths (-)") +
  ggtitle("Age Vs Total Number of Deaths") +
  ThemeMain
```

## Impact of Weather on the spread of Covid-19
When the pandemic first started, there was a wide speculation about the role of
weather on the spread of the virus. Therefore, with the available data, the 
relationship between weather params such as average temperature, maximum 
temperature, maximum temperature and precipitation was tested in this study. 

To keep the report length in check, only the correaltion between average
temperature and number of confirmed cases is presented in this report. 

```{r warning=FALSE}
time_province_covid_weather <- time_province_dt[province!="Sejong"][date != as.Date("2020-06-30")]
time_province_covid_weather <- time_province_covid_weather[,`:=`(confirmed_d2d=c(confirmed[1],diff(confirmed)),
                                                                 released_d2d=c(released[1],diff(released)),
                                                                 deceased_d2d = c(deceased[1],diff(deceased))),
                                                           by=.(province)]

weather_2020_dt <- weather_dt[date >= as.Date("2020-01-20")]

# merge weather and province data
#rm(weather_covid_province_dt)
weather_covid_province_dt <- merge(weather_2020_dt,time_province_covid_weather,by=c("date","province"),all=T)

avgTemp_confirmed_cor <- weather_covid_province_dt[,cor.test(avg_temp,confirmed_d2d,method="spearman")]

ggplot(weather_covid_province_dt,aes(confirmed_d2d,avg_temp)) + 
  geom_point() + 
  geom_smooth(method=lm) + 
  geom_label(x=5,y=5,label=paste("Spearman=",round(avgTemp_confirmed_cor$estimate,2)))+ 
  xlab("Number of Confirmed Cases") + 
  ylab("Average Temperature (°C)") + 
  ggtitle("Correlation between Average Temperature and the Number of infections") +
  ThemeMain
```

There is no significant correlation between average temperature and the number
of confirmed cases. The same behaviour was observed for other weather parameters



# References

1. https://en.wikipedia.org/wiki/Coronavirus_disease_2019

2. Coronavirus Disease 2019 (COVID-19)". U.S. Centers for Disease Control and Prevention (CDC). 11 February 2020. Retrieved 6 December 2020.

3. Transmission of SARS-CoV-2: implications for infection prevention precautions". World Health Organization (WHO).

4. https://en.wikipedia.org/wiki/Data_analysis

5. https://www.kaggle.com/kimjihoo/coronavirusdataset

6. https://en.wikipedia.org/wiki/Spearman%27s_rank_correlation_coefficient